Predicting Remaining Useful Life of NASA Aircraft Engines

### 2025-03-04 index.qmd
Updated methodology

CPH relies on data that has a time to event component and covariates for
that event.

@@

@@

$H_0$: the predictor's coefficient does not vary with time

$H_1$: the predictor's coefficient does vary with time

@@

$$
h(t|\mathbf{Z}) = h_0(t)\text{exp}(\sum_{k=1}^{p} \beta_kZ_k)
$$ {#eq-hazard}

$$
\frac{h(t|\mathbf{Z})}{h(t|\mathbf{Z}^*)} = \frac{h_0(t)\text{exp}(\Sigma_{k=1}^{p} \beta_kZ_k)}{h_0(t)\text{exp}(\Sigma_{k=1}^{p} \beta_kZ_k^*)} = \text{exp}[\sum_{k=1}^p \beta_k(Z_k-Z_k^*)]
$$ {#eq-hazardsratio}

@@

@@

>>>>

To determine whether to use CPH for modeling, the data must contain a
time to event value and meet various assumptions, including proportional
hazards. Data that is censored will require a survival analysis that
type of analysis is deliberately designed for censored data. The data
must also have a binary indicator variable for the event occurrence and
no missing values [@nahhas2025].

**General Equation**

$$ h(t|\mathbf{Z}) = h_0(t)\text{exp}(\sum_{k=1}^{p} \beta_kZ_k) $$

This equation can then be adapted for the specific dataset being
studied.

**Hazards Ratio**

$$ \frac{h(t|\mathbf{Z})}{h(t|\mathbf{Z}^*)} = \frac{h_0(t)\text{exp}(\Sigma_{k=1}^{p} \beta_kZ_k)}{h_0(t)\text{exp}(\Sigma_{k=1}^{p} \beta_kZ_k^*)} = \text{exp}[\sum_{k=1}^p \beta_k(Z_k-Z_k^*)] $$

**Kaplan-Meier**

Before generating the CPH model, it is beneficial to look at the
Kaplan-Meier curve. The Kaplan-Meier estimate ...

**CPH Model**

To generate the CPH model, a survival object must first be created.
Using the R package `survival`, the suvival formula can be generated by
running `Surv(time, event) ~ x`. That formula is then applied to the R
function `coxph(formula, data=)` which will generated the CPH model
[@R-base].

@@

For the CPH model to be valid, the following assumptions must be met. If
they are not met, the data must either be transformed.

@@

$$
\begin{align*}
H_0&: \text{the predictor's coefficient does vary with time} \\
H_1&: \text{the predictor's coefficient does not vary with time}
\end{align*}
$$

@@

@@

**Predictors**

Hypothesis test and wording for the significance of the predictors.

**Concordance Index**

@@

### Predictions
